---
title: "Anonymize csv files"
output: html_notebook
---

All files up to date as of 7/4/2025. Potential future updates:
- Check to see if a file already exists that you are trying to run? Does the anonymized file exist and check that an overwrite is fine.
- Move the original files to another folder location??
- Productionize the file (start/end times, secrets file, etc.)

## Libraries

```{r}
library(tidyverse)
library(lubridate)
library(googlesheets4)
```

## Google Drive Data

### Connection

```{r include=FALSE}
gs4_auth(email = "") # , cache = TRUE
# gs4_auth(cache = ".secrets", email = TRUE, use_oob = TRUE)

```

### Data sets

```{r}
sheet_id = "194KKu7z0YYAiBHWh4R0D57GGumSyY9Stc_ssCry2uDA"

member_anon_init = range_read(sheet_id, sheet = "members", col_types = 'iccccD')

# member_group_anon_init = range_read(sheet_id, sheet = "groups", col_types = 'iccDD')

remove(sheet_id)
```

## CSV Raw Data Sets

### Manually Select Files

Member contact information first

Member Deliveries second

```{r}

contact_loc = choose.files(default = "", caption = "Select the CONTACT file to anonomyze.")
stopifnot(str_detect(contact_loc, 'Member Contact Info') == TRUE) #making sure the right file was selected

delivery_loc = choose.files(default = "", caption = "Select the DELIVERY file to anonomyze.")
stopifnot(str_detect(delivery_loc, 'Past Deliveries') == TRUE) #making sure the right file was selected
```

### Pull Date information and check consistency

```{r}
contact_loc
delivery_loc

dash_start_contact = str_locate(contact_loc,'__')[1]
dash_start_del = str_locate(delivery_loc,'__')[1]

contact_date = str_sub(contact_loc, dash_start_contact-10, dash_start_contact-1)
del_date = str_sub(delivery_loc, dash_start_del-10, dash_start_del-1)

del_date_range = str_sub(delivery_loc, str_locate(delivery_loc,'(Quantity)')[1]+9)

stopifnot(contact_date == del_date) #making sure the files have the same capture date

```

### Pull Data sets

```{r}
members_raw = read_csv(contact_loc) |>  #, stringsAsFactors=FALSE unsure if this addition helped or hurt the process??
  mutate(file_date = ymd(contact_date))

deliveries_raw_short = read_csv(delivery_loc, n_max = 0)

deliveries_raw_dot = read.csv(delivery_loc) #, stringsAsFactors=FALSE unsure if this addition helped or hurt the process??

colnames(deliveries_raw_dot) = colnames(deliveries_raw_short)

deliveries_raw = deliveries_raw_dot |> 
  mutate(file_date = ymd(del_date)) |> 
  filter(`First Name` != '' & `Last Name` != '' & Email != '') #removing the total and blank rows.

# deliveries_raw_t_test = deliveries_raw_t |> 
#   filter(`Last Name` == 'Rathert')
```

### Members in Delivery output missing

```{r}
members_anon_check_init = members_raw |> 
  rename_with(tolower) |> 
  rename_with(make.names) |> 
  select(route, pickup_site = pickup.site, file_date, first_name = first.name, last_name = last.name, email) |> 
  mutate(concat_member = paste0(first_name, "||", last_name, "||", email))

deliveries_anon_check_init = deliveries_raw |> 
  rename_with(tolower) |> 
  rename(delivery_date = 'delivery date', first_name = 'first name', last_name = 'last name', zip_code = 'zip code') |> 
  mutate(concat_member = paste0(first_name, "||", last_name, "||", email),
         route = NA,
         pickup_site = NA) |> 
  filter(concat_member != 'NA||NA||NA') |> 
  select(route, pickup_site, file_date, first_name, last_name, email, concat_member) |> 
  distinct() |> 
  left_join(members_anon_check_init |>
              select(concat_member) |> 
              mutate(present = 1)
              , by = c('concat_member')) |> 
  filter(is.na(present)) |> 
  select(-present)

all_members_anon_check = members_anon_check_init |> 
  rbind(deliveries_anon_check_init)

# checking to make sure no duplicate member information
stopifnot((all_members_anon_check |> 
             select(first_name, last_name, email) |> 
             group_by_all() |> 
             summarise(max = n()) |> 
             filter(max > 1) |> 
             pull()) == 0)

missing_member_id = all_members_anon_check |> 
  left_join(member_anon_init |> 
              select(member_id, concat_member)
            , by = c('concat_member')
            ) |> 
  filter(is.na(member_id)) |> 
  mutate(initial_date = ymd(contact_date))

random_sample = nrow(missing_member_id) + 1000 

sample_df = data.frame('member_id' = 1:random_sample)

sample_new = sample_df |> 
  left_join(member_anon_init |> 
              mutate(present = 1) |> 
              select(member_id, present) |> 
              distinct() 
            , by = c('member_id')
  ) |> 
  filter(is.na(present))

sample_new$order <-  runif(nrow(sample_new),min = 0, max=1)

sample_new_final = sample_new |> 
  arrange(order) |> 
  select(-present, -order) |> 
  rowid_to_column("id")

member_anon_new = member_anon_init |> 
  rbind(missing_member_id |> 
          select(first_name, last_name, email, concat_member, initial_date) |> 
          rowid_to_column("id") |> 
          left_join(sample_new_final
                    , by = c('id')
                    ) |> 
          select(-id)|> 
          relocate(member_id)) |> 
  arrange(member_id)

# checking to make sure no duplicate member_ids
stopifnot((member_anon_new |> 
             select(member_id) |> 
             group_by_all() |> 
             summarise(max = n()) |> 
             filter(max > 1) |> 
             pull()) == 0)

# only uncomment this when this process is fully ready...

sheet_id = "194KKu7z0YYAiBHWh4R0D57GGumSyY9Stc_ssCry2uDA"

sheet_write(member_anon_new, sheet_id, sheet = "members")

remove(sheet_id)

```


## Clean and Anonymize Data Set

### Member Contact Information

```{r}
members_home_del = members_raw |> 
  rename_with(tolower) |> 
  rename_with(make.names) |> # NEED TO BUILD IN CLEANING LOGIC FOR HOME DELIVERY MEMBERS... Eventually as well as Trial members
  mutate(pickup.site = trimws(pickup.site),
         last.name = trimws(last.name),
         site_length = str_length(pickup.site),
         name_length = str_length(last.name),
         home_delivery = str_detect(pickup.site, "Home Delivery -"),
         pickup_detail_v1 = ifelse(home_delivery == TRUE, str_sub(pickup.site, site_length - 3, site_length), NA),
         pickup_detail_v2 = ifelse(home_delivery == TRUE, str_sub(last.name, name_length - 3, name_length), NA)
         ) 

members_home_del |> filter(home_delivery == TRUE) |> select(pickup_detail_v1) |> distinct()

#check to make sure the member last name home delivery short name matches to the pick up short description
stopifnot(members_home_del |> 
  mutate(check = pickup_detail_v1 == pickup_detail_v2) |> 
  filter(check == FALSE | 
           (is.na(pickup_detail_v1) & !is.na(pickup_detail_v1)) | 
           (!is.na(pickup_detail_v1) & is.na(pickup_detail_v1))
         ) |> 
  summarise(n = n()) |> 
  pull() == 0)

members_init = members_home_del |> 
  mutate(last.name = trimws(ifelse(!is.na(pickup_detail_v1), str_replace(last.name, pickup_detail_v1, ''), last.name)),
         pickup.site = ifelse(home_delivery == TRUE, paste0('Home Delivery - ',pickup_detail_v1), pickup.site)
         ) |> 
  select(-site_length, -name_length, -pickup_detail_v1, -pickup_detail_v2) |> 
  mutate(concat_member = paste0(first.name, "||", last.name, "||", email)) |> 
  select(route, pickup_site = pickup.site, file_date, concat_member) 

members_anon = members_init |> 
  full_join(member_anon_new |>
              select(member_id, concat_member)
              , by = c('concat_member')) |> 
  select(-concat_member)
```


### Member Deliveries

```{r}
deliveries_init = deliveries_raw |> 
  # rename_with(tolower) |> 
  rename(delivery_date = 'Delivery Date', first_name = 'First Name', last_name = 'Last Name', 
         email = Email, address = Address, city = City, zip_code = 'Zip Code', state = State) |> 
  mutate(concat_member = paste0(first_name, "||", last_name, "||", email)) |>
  relocate(concat_member) |> 
  filter(concat_member != 'NA||NA||NA') |> 
  select(-address, -city, -zip_code, -state) # -first_name, -last_name, -email, 

deliveries_init_anon = deliveries_init |> 
  left_join(member_anon_new |>
              select(member_id, concat_member)
              , by = c('concat_member')) |> 
  relocate(member_id, file_date) 

deliveries_anon_check = deliveries_init_anon |> 
  filter(is.na(member_id)) |> 
  select(first_name, last_name, email, concat_member) |> 
  distinct()

stopifnot(deliveries_anon_check |> 
            summarise(n = n()) |> 
            pull() == 0
)

deliveries_anon = deliveries_init_anon |> 
  select(-concat_member, -first_name, -last_name, -email)

# deliveries_anon_check_ind = deliveries_init_anon |>
#   filter(member_id %in% c(99,467))
```

### Member Deliveries Pivot Long

```{r}
farmigo_columns = deliveries_anon |> 
    colnames() |> 
  as.data.frame() |> 
  mutate(col_name = colnames(deliveries_anon)) |> 
  select(-'colnames(deliveries_anon)') |> 
  ungroup() |> 
  mutate(price_length = str_count(col_name)
         , price_str = str_sub(col_name, price_length - 6, price_length)
         , price = price_str == '- Price') |>  
  filter(!col_name %in% c('member_id','file_date','delivery_date')) 

farmigo_columns |> 
  group_by(price) |> 
  summarise(n = n())

## check to make sure equal price vs quantity columns
stopifnot(farmigo_columns |>
            group_by(price) |> 
            summarise(n = n()) |> 
             filter(price == TRUE) |> 
             pull()
             == farmigo_columns |> 
            group_by(price) |> 
            summarise(n = n()) |> 
             filter(price == FALSE) |> 
             pull() )

item_list = farmigo_columns |> 
  filter(price == FALSE) |> 
  select(col_name) |> 
  pull()

farmigo_del_cln_sales = deliveries_anon |> 
  select(member_id, file_date, delivery_date, 
         all_of(item_list)) |> 
  pivot_longer(cols = -c(member_id, file_date, delivery_date)
               , names_to = "item"
               , values_to = "sales")

farmigo_del_cln_price = deliveries_anon |> 
  select(-file_date, member_id, delivery_date,
         -all_of(item_list)) |> 
  pivot_longer(cols = -c(member_id, delivery_date)
               , names_to = "item"
               , values_to = "price") |> 
  mutate(item = str_sub(item, 0, str_count(item)-8))

farmigo_del_cln = farmigo_del_cln_sales |> 
  left_join(farmigo_del_cln_price
            , by = c('member_id', 'delivery_date', 'item')) |> 
  filter(!is.na(sales) | !is.na(price)) |> 
  # mutate(total = sales*price) |> 
  rename(item_unit = item)

stopifnot(farmigo_del_cln |> 
            filter(is.na(sales)) |> 
            summarise(n = n()) |> 
            pull() == 0
  )

stopifnot(farmigo_del_cln |> 
            filter(is.na(price)) |> 
            summarise(n = n()) |> 
            pull() == 0
  )

# farmigo_del_cln_check = farmigo_del_cln |>
#   filter(member_id %in% c(99,467))
# 
# farmigo_del_cln_sales_check = farmigo_del_cln_sales |> 
#   filter(member_id %in% c(99,467)) 
# 
# farmigo_del_cln_price_check = farmigo_del_cln_price |> 
#   filter(member_id %in% c(99,467))

```



## Create CSV files and upload to Repo

### Member Contact Information

```{r}
repo_location = 'C:/Users/Fair Shares/Documents/_ds_fairshares/Farmigo_Database/step_1_anonymization/Raw/'
## repo_location = 'C:/Users/Fair Shares/Documents/_ds_fairshares/Farmigo_Database/step_1_anonymization/Raw/'

write.csv(members_anon
          , paste0(repo_location, 'contacts/', contact_date, '__member_contact_info_all.csv')
          , row.names = FALSE)
```

### Member Deliveries

```{r}
write.csv(farmigo_del_cln
          , paste0(repo_location, 'member_deliveries/', del_date, '__member_past_deliveries',del_date_range)
          , row.names = FALSE)
```

### Move Temp Files to backup folder

```{r}

```


```{r}
# gs4_deauth()
```


